Workload Analysis of Autonomous Driving System: Apollo, Baidu Inc.

### 2019-04-23 paper/template/paper.tex
Finished camera

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{dblfloatfix}
\usepackage{inputenc}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\begin{figure*}[t]
    \centering
    \includegraphics[height=3.7cm]{images/apollo_software_architecture.png}
    \caption{Apollo Software Architecture}
    \label{apollo_software_architecure}
\end{figure*}

\begin{figure*}[b!]
    \centering
    \includegraphics[height=3.7cm]{images/perception_software_architecture.png}
    \caption{Perception Software Architecture}
    \label{perception_software_architecture}
\end{figure*}

@@

The Fusion Camera Detection applies a sequence of tasks, called Obstacle Camera Pipeline, to camera frames.
The pipeline is composed by lanes detection and post-processing, obstacles tracking and obstacles detection and post-processing.
The pipeline is not applied equally to each frame; lanes detection and post-processing are only applied to camera frames coming from the 6mm camera, due to the wider perspective.

@@

\subsubsection*{Complexity}
Explain the complexity of the tasks and their dependencies
\subsubsection*{Response time}
Response time analysis and on which device each task runs.
Table or graph about response times.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{dblfloatfix}
\usepackage{subcaption}
\usepackage{adjustbox}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\begin{figure*}[t]
    \centering
    \includegraphics[height=2.5cm]{images/apollo_software_architecture.png}
    \caption{Apollo Software Architecture}
    \label{apollo_software_architecure}
\end{figure*}

\begin{figure*}[b!]
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth, height=2.5cm]{images/perception_software_architecture.png}
        \caption{Perception Software Architecture}
        \label{perception_software_architecture}
    \end{subfigure}
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth,height=2.5cm]{images/obstacle_camera_pipeline.png}
        \caption{Obstacle Camera Pipeline}
        \label{obstacle_camera_pipeline}
    \end{subfigure}
    \caption{}
\end{figure*}

%\begin{figure}[b!]
%    \centering
%    \includegraphics[height=2.5cm]{images/perception_software_architecture.png}
%    \caption{Perception Software Architecture}
%    \label{perception_software_architecture}
%\end{figure}
%
%\begin{figure}[b!]
%    \centering
%    \includegraphics[height=2.5cm]{images/obstacle_camera_pipeline.png}
%    \caption{Obstacle Camera Pipeline}
%    \label{obstacle_camera_pipeline}
%\end{figure}

@@

The Fusion Camera Detection applies a sequence of tasks, called Obstacle Camera Pipeline to camera frames, displayed in Figure \ref{perception_software_architecture}.
The pipeline is composed by lanes detection and post-processing, obstacles tracking and obstacles detection and post-processing.
The pipeline is not applied equally to each frame; lanes detection and post-processing are only applied to camera frames coming from the 6mm camera, due to the wider perspective.

@@

\subsubsection*{Complexity}

The computational complexity of the whole pipeline is dominated by CNN inferences.
Lanes detection, in addition, depends on image resizing and the fusion of detected lanes into one frame.
Lanes post-processing performs several operations on lane points of each lanes detected and the iterative RANSAC algorithm to find the polynomial coefficients.
The tracker prediction relies only to the past obstacles detected and the update of the Adaptive Kalman Filter.
The obstacles detection, similarly to the lane detection, resizes the image and performs some refinements on the obstacles candidates to refine their bounding boxes.
The obstacles post-processing and tracking association involve the comparison between past obstacles and current obstacles.

\begin{table}[htbp]
    \begin{center}
    \begin{adjustbox}{max width=\columnwidth}
        \setlength{\tabcolsep}{0.5em}
        \renewcommand{\arraystretch}{1.2}
        \begin{tabular}{|p{3cm}|p{6cm}|}
            \hline
            \textbf{Task} & \textbf{Complexity} \\
            \hline
            Lanes Detection & CNN inference, image resizing and single lanes frame\\
            \hline
            Lanes Post-processing & RANSAC algorithm, lane points x lanes detected \\
            \hline
            Tracker Prediction & Past obstacles detected\\
            \hline
            Obstacles Detection & CNN inference, image resizing, obstacles candidates, obstacles detected\\
            \hline
            Obstacles Post-processing & Obstacles detected\\
            \hline
            Tracker Association & Obstacles detected x past obstacles\\
            \hline
            \end{tabular}    
    \end{adjustbox}
    \label{fusion_detection_component_complexity_table}
    \end{center}
    \caption{Fusion Camera Detection Complexity}
\end{table}

\subsubsection*{Response time}

The average response time of the component in our simulation is 49.76 ms and the 95.86\% of time is spent on CNN inferences.
This dominance of CNN inferences lead to make the computation independent from the number of obstacles detected, even if the pre- and post-processing operations are needed to generate a correct detection.
This component heavily relies on GPU for the CNN inferences, image resizing, the extraction of the obstacles bounding boxes from the YoloNet output and the similarities between obstacles and frames in the tracking phase.

\begin{table}[htbp]
    \begin{center}
    \begin{adjustbox}{max width=\columnwidth}
        \setlength{\tabcolsep}{0.5em}
        \renewcommand{\arraystretch}{1.2}
        \begin{tabular}{|l|r|r|}
            \hline
            \textbf{Task}&\multicolumn{2}{|c|}{\textbf{Response Time}} \\
            \cline{2-3} 
            & \textbf{\textit{ms}}& \textbf{\textit{\%}}\\
            \hline
            Lanes Detection & 38.14 & 76.65\\
            \hline
            Lanes Post-processing & 0.72 & 1.45 \\
            \hline
            Tracker Prediction & 0.01 & 0.02\\
            \hline
            Obstacles Detection & 9.56 & 19.21\\
            \hline
            Obstacles Post-processing & 0.6 & 1.2\\
            \hline
            Tracker Association & 0.73 & 1.47\\
            \hline
            \end{tabular}    
    \end{adjustbox}
    \label{fusion_detection_component_response_time_table}
    \end{center}
    \caption{Fusion Camera Detection Response Time}
\end{table}
